{\small Filamentary transport in high-power H-mode conditions and in no/small-ELM regimes to predict heat and particle loads on PFCs for future devices}

### 2017-11-14 Meetings/GPMNov2017/gpm_november2017_topic21.tex
Update to PDF slides
Final amendment to slides

\begin{frame}{Compare fueling with/without cryopumps}
\Fontvi
  \vspace{-1cm}
\begin{columns}
  \begin{column}{0.65\textwidth}
    \centering{\includegraphics<1>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/CompareShot34276_34278}}
    \centering{\includegraphics<2>[height=.65\textheight]{../../Experiments/AUG/analysis/pdfbox/PuffingIpolsola34276_34278}}
    \only<3>{
    \begin{tikzonimage}[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/EvolutionEdgeProfiles_34276_34278}
      \draw [->, ultra thick, white] (0.2, 0.45) -- (0.3, 0.55);
      \draw [->, ultra thick, dashed, red] (0.62, 0.45) -- (0.72, 0.55);
    \end{tikzonimage}}
  \centering{\includegraphics<4>[height=.85\textheight]{../../Experiments/AUG/analysis/pdfbox/Shot_34276_34278_InterELMprofiles}}
  \end{column}
  \begin{column}{0.35\textwidth}
    \begin{itemize}
    \item<1-> Same fueling but with cryo-pumps
      \item<1-> H-5 density is different and remain constant, both
        divertor and midplane pressure are reduced (to 1/3
        approximately) no sign of detachment
      \item<2-> Different ELMy regimes reached with reduced size and
        increased frequency without the cryopumps
      \item<3-> Also with this amount of fueling weaker indication of SOL
        saturation observed as confirmed by Li-Beam and by RIC (Antenna 4)
      \item<4> Inter-ELM resolved profile suggest a flattening even
        with the cryompumps still even though $\Lambda_{div}$ is
        marginal above 1 only in the near SOL

@@

\begin{frame}{Program for 2018: AUG}
  \begin{itemize}
     \item X-point manipulator (NPH ?) simultaneously with MEM
     \item X-point vertical shift in order to have SP at different
	vertical height at the target. \alert{We will observe similar
          observation as obtained in JET when moving from horizontal
          to vertical target?}
     \item DN discharges. With slow movement of the second X-point into the vessel
	to be performed at constant power/density where shoulder
        alreay exists. \alert{This is mandatory to complement the
          information obtained on TCV}
     \item USN with midplane/X-point manipulator to monitor the
       upstream SOL 
     \item Heat load
\end{itemize}
 \end{frame}
 \begin{frame}{MST2-NPH}
   \begin{columns}
     \begin{column}{0.5\textwidth}
       \centering{\includegraphics[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/NPH_2018}}
     \end{column}
     \begin{column}{0.5\textwidth}
       \begin{itemize}
         \item MST2 founded project for the realization of a New Probe
           Head (NPH) (C. Ionita,  B. Schneider \textit{et al})
         \item Simultaneous information on Ion temperature (2 RFAs),
           Plasma potential and electron temperature (Emissive probe
           coupled with floating potential) and magnetic fluctuations
           from 2 3-axial magnetic pick up coil
         \item Potentially tested on TCV beginning of 2018 and then
           moved to other MST1 devices
       \end{itemize}
     \end{column}
   \end{columns}
 \end{frame}

\begin{frame}{Program for 2018: TCV}
  \begin{itemize}
     \item \textcolor{consorziored}{H-Mode} 
      \item Long divertor legs (probe in the lower port) to check if
        increase of filamentary transport along the divertor leg
        exists in high density scenarios
      \item \textcolor{taorange}{SnowFlake to monitor the fluctuations in between the 2 separatrix
	to be done in high density discharges}
       \item \textcolor{taorange}{Try to move the second X-point in SN divertor at a different
	Z position while keeping the same radial distances between the
	points}
\end{itemize}
\end{frame}

@@

\begin{frame}{Code requirements}
  \begin{itemize}
    \item Dedicated simulations with first principles codes (GBS,
      HESEL)
    \item Check if trends can be reproduced
    \item potential input for future experiments regarding role of
        f.x. neutrals and recycling
  \end{itemize}
\end{frame}
\end{document}

>>>>

\begin{frame}{Compare fueling with/without cryopumps}
\Fontvi
  \vspace{-1cm}
\begin{columns}
  \begin{column}{0.65\textwidth}
    \centering{\includegraphics<1>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/CompareShot34276_34278}}
    \centering{\includegraphics<2>[height=.65\textheight]{../../Experiments/AUG/analysis/pdfbox/PuffingIpolsola34276_34278}}
    \only<3>{
    \begin{tikzonimage}[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/EvolutionEdgeProfiles_34276_34278}
      \draw [->, ultra thick, white] (0.2, 0.45) -- (0.3, 0.55);
      \draw [->, ultra thick, dashed, red] (0.62, 0.45) -- (0.72, 0.55);
    \end{tikzonimage}}
  \centering{\includegraphics<4>[height=.85\textheight]{../../Experiments/AUG/analysis/pdfbox/Shot_34276_34278_InterELMprofiles}}
  \end{column}
  \begin{column}{0.35\textwidth}
    \begin{itemize}
    \item<1-> Same fueling but with cryo-pumps. \alert{To check role
        of neutral density in H-Mode}
      \item<1-> H-5 density is different and remain constant, both
        divertor and midplane pressure are reduced (to 1/3
        approximately) no sign of detachment
      \item<2-> Different ELMy regimes reached with reduced size and
        increased frequency without the cryopumps
      \item<3-> Also with this amount of fueling weaker indication of SOL
        saturation observed as confirmed by Li-Beam and by RIC (Antenna 4)
      \item<4> Inter-ELM resolved profile suggest a flattening even
        with the cryompumps still even though $\Lambda_{div}$ is
        marginal above 1 only in the near SOL

@@

\begin{frame}{Program for 2018: AUG}
  \begin{itemize}
     \item X-point manipulator (NPH ?) simultaneously with MEM
     \item X-point vertical shift in order to have SP at different
	vertical height at the target. \alert{We will observe similar
          observation as obtained in JET when moving from horizontal
          to vertical target or during horizontal target SP sweeping?}
     \item DN discharges. With slow movement of the second X-point into the vessel
	to be performed at constant power/density where shoulder
        alreay exists. \alert{This is mandatory to complement the
          information obtained on TCV}
     \item USN with midplane/X-point manipulator to monitor the
       upstream SOL 
     \item Heat load
\end{itemize}
 \end{frame}
 \begin{frame}{MST2-NPH}
   \begin{columns}
     \begin{column}{0.5\textwidth}
       \centering{\includegraphics[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/NPH_2018}}
     \end{column}
     \begin{column}{0.5\textwidth}
       \begin{itemize}
         \item MST2 founded project for the realization of a New Probe
           Head (NPH) (C. Ionita,  B. Schneider \textit{et al})
         \item Simultaneous information on Ion temperature (2 RFAs),
           Plasma potential and electron temperature (Emissive probe
           coupled with floating potential) and magnetic fluctuations
           from 2 3-axial magnetic pick up coil
         \item Potentially tested on TCV beginning of 2018 and then
           moved to other MST1 devices
       \end{itemize}
     \end{column}
   \end{columns}
 \end{frame}

\begin{frame}{Program for 2018: TCV}
  \begin{itemize}
     \item \textcolor{consorziored}{H-Mode} 
      \item \textcolor{ta2orange}{Long divertor legs (probe in the lower port) to check if
        increase of filamentary transport along the divertor leg
        exists in high density scenarios}
      \item \textcolor{gray}{SnowFlake to monitor the fluctuations in between the 2 separatrix
	to be done in high density discharges}
       \item \textcolor{gray}{Try to move the second X-point in SN divertor at a different
	Z position while keeping the same radial distances between the
	points}
\end{itemize}
\end{frame}

@@

\begin{frame}{Code requirements}
  \begin{itemize}
    \item Dedicated simulations with first principles codes (GBS,
      HESEL)
    \item Check if trends can be reproduced
    \item Potential input for future experiments regarding role of
        f.x. neutrals and recycling
  \end{itemize}
\end{frame}
\end{document}
